---
output: pdf_document
title: New York Toy Agency report of Baby Names
author: Liam Andrew Beattie 
---

# To what degree do names persist into the future?


```{r Setup, Include=FALSE,echo=FALSE,message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
rm(list = ls()) # Clean your environment:

library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
import_multiple_rds()
```

```{r ranking baby names, include=FALSE}
rankednames <- Baby_Names_By_US_State %>% get_name_rank_per_gender_n_year() %>% #ranking baby names to compute spearman correlation,Rankings are done on all names of that year, per gender.
    add_growth_of_name_variable() #growths are used to isolate biggest growths year on year
```

Figure \ref{spearplot} highlights how names tend to persist into the future by visually showing the longevity of naming trends by providing annual Spearman rank correlation results for each gender, as well as a general non-linear time trend. Through the social security records we find a general time trend that naming longevity tends to decrease year-on-year. Therefore this graph illustrates why the toy company must invest more in predicting baby names based on pop culture.  

Interestedly, since the 1990s the Spearman rank correlation for boys has generally decreased while for girls it actually has generally increased.


```{r Spearman Correlation Plot, fig.cap="Spearman Correlation\\label{spearplot}",warnings=FALSE}
rankednames %>%    plot_spearman_graph()
```


\newpage

# What influences popularity? 


Figure \ref{growthbaby} shows time trends of select baby names and their popularity in the United States graphed against the date. The 15 names selected were the 15 top names who experienced the biggest jump in name adoption from one year to the next. This growth rate of name adoption was calculated using the following formula:
\[
\text{Growth Rate} = \left( \frac{\text{Total Count}_{\text{current}} - \text{Total Count}_{\text{previous}}}{\text{Total Count}_{\text{previous}}} \right) \times 100
\]

Interestingly, my older supervisor correctly remembered the name fad from the "Where the Heart Is" craze, as in 1974, there was a notable spike in the number of little girls being named Katina. This should underscore the point that parents lack creativity, and seldom not make up random names from thin air when naming their child, but rather turn to pop culture for a sizeable influence.   


```{r ridge plots,warning=FALSE,fig.cap="Biggest Year-on-Year growth for Baby Names\\label{growthbaby}"}

rankednames %>%
    get_top_n_growth_names(15,TOP = 120) %>% 
    fill_missing_years() %>% 
    plot_ridge_names()
    

```


To test this theory that parents are influenced by pop culture, I took the 15 top names found above and investigated if any names showed up in the Billboard's top 100 songs chart for the previous year. Notable two names were found, Ashanti who had a hit song with Ja Rule in 2001, causing a spike name spike in 2002, and Dierks Bentley who caused a name spike in 2010. 


```{r table of names that are found in music charts}
unique((rankednames %>% get_top_n_growth_names(15,TOP = 120))$Name) %>% 
    find_top_names(rankednames,charts) %>% 
    knitr::kable()
```





