---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Indian Olympics Overview"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Liam Andrew Beattie"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Data Science Exam, Stellenbosch University" # First Author's Affiliation
Email1: "22562435\\@sun.ac.za" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
 # nocite:  
 # @oecd_cpi_japan for CPI 
 # @oecd_monetary_aggregates_japan 
 # @oecd_production_volume_japan 
 # @oecd_interest_rates_japan | # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
import_multiple_rds("data/olympics/.")
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->


```{r, include=FALSE}
data<-join_olympics(winter, summer) %>% 
    metal_weightings_summation() %>% 
    left_join(GDP, by = c("Country" = "Code")) 

```


Figure \ref{fig1} that in the summer Olympics, India has faired better than most other countries who have similar GDP per Capita values than them. Additionally, they tend to fair better than than most South American countries, barring Brazil. Furthermore, the Figure includes country codes for countries who "punch above their weight", this allocation is to countries who manage to win a high number of medals despite have a lower GDP per Capita. 


```{r, fig.cap="Olympic Medals vs GDP per Capita\\label{fig1}"}

data %>% plot_olympics_points()

```



One of my favourite Olympic sports is boxing. Interestingly, boxing unlike many other Olympic sports, is dominated by countries who have low GDP per capita. Figure \ref{fig2} shows that sports that do not require participants do be punched in the face, have winners who are from countries with high GDP per Capita values.


```{r,fig.cap="Boxing winners GDP per Captia versus wealthier sports \\label{fig2}"}

sports<-c("Boxing","Skating","Roque","Rackets","Golf","Ice Hockey") #these are the sports to compare

summer %>% attach_simple_metal_weightings() %>%
    group_by(Country, Sport) %>%
    summarise(Medals = sum(medal_weighting, na.rm = TRUE),
              .groups = 'drop') %>%
    left_join(GDP, by = c("Country" = "Code")) %>%
    filter(Sport %in% sports) %>%
    plot_sport_points_gdpandmedals()
    


```

Below in Figure \ref{fig3} is a Heatmap of countries who dominate Olympic events. 


```{r,fig.cap="Heat Map of Olympic Dominance: Summer and Winter\\label{fig3}"}
create_combined_plot(summer, winter)

```



